Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Remove TBD
Terminology: explain /spec/

\begin{abstract}
We observed that several widely used Haskell libraries do not have
tests.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
Doctest for user documentation and
Hspec for code documentation.
Our approach can be used for design, documentation and automated
testing.  We hope that this motivates Haskell programmers to write
more and better tests.

TBD:

\begin{itemize}
    \item We show how to reuse pieces of specifications (and/or that
        specifications are composable?).
\end{itemize}

\begin{itemize}
    \item State the problem.
    \item Say why it's an interesting problem.
    \item Say what your solution achieves.
    \item Say what follows from your solution.
\end{itemize}

\end{abstract}

@@

The definitions of words used in this paper is as follows:

@@

\item[spec]
    TBD: BDD terminology for test suite.
\end{description}

>>>>

\begin{abstract}
We observed that several widely used Haskell libraries do not have
tests.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
Doctest for user documentation and
Hspec for code documentation.
Our approach can be used for design, documentation and automated
testing.  We hope that this motivates Haskell programmers to write
more and better tests.
\end{abstract}

@@

We use the following terminology:

@@

\item[spec]
    A spec is similar to a test suite in TDD.  But it is written with
    specification terminology, and produces a specification document
    when run.
\end{description}
